Selective electroporation of the viral envelope via optimal control of transmembrane potential

### 2021-06-22 documents/pure_electroporation.tex
Gradient bang-bang switching time method, and perhaps Fourier method

\title{Selective electroporation of the viral envelope via optimal control of transmembrane potential}
\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216}}\footnote{Ontario, Canada; contact information in the ORCiD.}}
\date{\small{March 21 2021}}

@@

	This minor transposition was only detected late in the project, and so some documentation may still contain the incorrect coefficients. Beware.

@@

@@

@@

\begin{tcolorbox}
	First instinct might be to try to solve for the waveform that sets alpha beta gamma to zero. 
\end{tcolorbox}

Written in texst

@@

\section*{Limitations and next steps}

@@

>>>>

\title{Selective electroporation of the viral envelope via optimal control of transmembrane potential}
\author{\footnotesize{Daniel Correia\orcidlink{0000-0002-9353-0216} \{dcorreia@whimsysciences.com || therobotist@gmail.com\}
		 \href{https://0xdbfb7.com/email_pledge.txt}{Please don't hesitate to contact; see here}}\footnote{Ontario, Canada; contact information in the ORCiD.}}
\date{\small{March 21 2021}}

@@

	This minor transposition was only detected late in the project, so some documentation in the repository may still contain the incorrect coefficients. Beware.

@@

a double integrator

@@

There are suprisingly many more quan

@@

\begin{tcolorbox}
	First instinct might be to try to solve for the waveform that sets alpha beta gamma to zero; feeding this though produces a reasonable solution []. 
\end{tcolorbox}

Puts much more effort into further analytical rearrangement before resorting to; by more fully using Pontryagin's Maximum Principle, and by formulating a control theoretic Hamiltonian. What looks to be a superb code hampath, did not have the experience to implement the hamiltonian at short notice.

\subsection*{Bang-bang control}

A good review of advanced bang-bang control techniques \cite{Computations2004}.

@@

\section*{Limitations and recommendations for further study}

@@

\section*{Commentary and discussion}

In easily mutable versions of this paper, this section will be

I have been lucky to have been provided the opportunity to conduct this research.
